%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Intern Technician II} % Job title
    {Keysight Technologies} % Organization
    {Santa Rosa, California} % Location
    {June 2020 - Aug. 2020 May 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Won Keysight's 2022 Hackathon with the SkyFox team by developing a payload for the Alta X drone to provide aerial spectrum analysis solutions. Personally developed the networking stack, flight stack, and webapp backend.}
        \item {Currently upgrading Graffy to be developed on a modern toolchain.}
        \item {Designed and manufactured the Hotpi PCB: a board containing 6 thermocouple-to-digital converters communicating to a Raspberry Pi via the SPI protocol. Currently creating a webapp to control the measurements.}
        \item {Manufactured spreadsheets for the Marketing department to identify the competitive comparison of individual products and processes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Developer} % Job title
    {ASU Research Enterprise} % Organization
    {Tempe, Arizona} % Location
    {May 2021 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and designed cybersecurity labs to teach Navy ROTC students the Linux command line, AWS System Administration and Cloud Computing, Drone/WiFi hacking, Penetration Testing Tools and Techniques, and Open Source Intelligence (OSINT).}
        \item {Created and managed secure and scalable AWS environment for military affiliated students.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}

